Flattering Advice: Avoiding Disappointment as a Driver of Gender Discrimination

### 2024-01-15 manuscript/manuscript.Rmd
Study 2 discussion

@@

## Discussion

# General Discussion

Advice substantially shapes people's career and personal outcomes.
Therefore, understanding advisers' motivations has far-reaching
implications. We propose that advisers' focus on advisees' expectations
and the desire to avoid disappointing them can induce gender differences
in the advice given and ultimately in the outcomes achieved. Gender
differences in career outcomes contribute significantly to the gender
wage gap, with women often holding less senior positions and
experiencing worse career outcomes, even with equal performance.
Therefore, identifying a factor such as expectations that contributes to
this gap has important implications for organizational practice.

>>>>

<!-- David: We should also report something on accuracy of the advice given across -->
<!-- the treatments. Even if no difference. -->

@@

## Discussion
In a context where advice communicates ego-relevant information (here, people's
attractiveness), we find that the advice people give is contingent on their
incentives. Specifically, when they get rewarded for being more likeable, they
recommend that the advisee bet on a more favorable rank than when they are
incentivized for accuracy. Importantly, advisees do not discount flattering
advice and instead evaluate people who advise them to bet on a more attractive
rank as warmer and more likeable. These gains to interpersonal perceptions do
not come at the cost of trustworthiness, even when the advice is substantially
inflated (e.g., a recommendation that the advisee is the most attractive in the group).

# General Discussion
Advice substantially shapes people's career and personal outcomes.
Therefore, understanding advisers' motivations has far-reaching
implications. We propose that advisers' focus on advisees' expectations
and the desire to avoid disappointing them can induce gender differences
in the advice given and ultimately in the outcomes achieved. Gender
differences in career outcomes contribute significantly to the gender
wage gap, with women often holding less senior positions and
experiencing worse career outcomes, even with equal performance.
Therefore, identifying a factor such as expectations that contributes to
this gap has important implications for organizational practice.
